---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# summarystats

<!-- badges: start -->
<!-- badges: end -->

The goal of summarystats is to calculate summary statistics for a given variable within a dataset, grouped by another variable. Below shows an example of its usage. Package dependency involves `dplyr`.

## Installation

You can install summarystats from Github by running:

``` r
devtools::install_github("https://github.com/stat545ubc-2023/summarystats")
```

## Examples

This example calculates the summary statistics for the dataset 'iris' for the variable `Sepal.Length` for each species:

```{r example}
library(summarystats)

sepal_length_summary <- calc_summary_stats(data = iris, grouping_variable = Species, data_variable = Sepal.Length)
print(sepal_length_summary)
```

This example calculates the summary statistics for the dataset `PlantGrowth` for the variable weight, grouped by the samples' treatment group.

```{r example 2}
library(summarystats)
plant_weight_summary <- calc_summary_stats(data = PlantGrowth, grouping_variable = group, data_variable = weight)
head(plant_weight_summary)

```

